Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex

\subsection{Experimental Results}
The tests were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1060 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; the cloud platform is deployed by OpenStack; and
the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0.

>>>>

\subsection{Experimental Results}
The tests were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1060 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; and the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0. In order to deploy an infrastructure as a service cloud,
we installed OpenStack Icehouse version and QEMU/KVM 0.12.1 as the hypervisor in one
of these 5-node cluster. A fully-featured OpenStack deployment usually requires
at least three nodes: one controller node that manages the compute nodes 
where the VMs are hosted, one network node that manages the logic
virtual network for the VMs, and one or more compute nodes that 
run the hypervisor and virtual machines. However, our OpenStack deployment
was deployed in one-node architecture making better use of our resources.
Thus, the main OpenStack services such as identity, image, compute, dashboard, and 
network services were installed in the first machine without GPU described above.
